\tname{}: Synthesis of Rules for Intrusion Detectors

### 2021-02-19 paper/old/paper.tex
organizing files

Figure~\ref{fig:adaptor-golden-rule.suricata} shows an example of an
http rule that captures traffic containing the string
\CodeIn{"/HtmlAdaptor"} in the payload.
Figure~\ref{fig:distribution-contents} shows the distribution of
number of content options per rule for the data set mentioned
above. We limited the number of content options per rule to 7 in the
histogram for space. \MyComment{Rules without \CodeIn{content} options
  are an exception and half of the rules contain at least two
  \CodeIn{content} options.}  To sum up, content options appear
frequently in http rules and rules may contain several of these
options. Handling content options is therefore very important.

@@

    %%Apache Struts 2 & \cite{wrccdc} & RCE & http & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\    
    ColdFusion \MyComment{PESC} & \cite{nikto} & PESC & http \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    iisadmin access\MyComment{web-application-attack} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    JBoss JMX\MyComment{ Console Beanshell Exploit} & \cite{nikto} & RCE & http \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    scripttag\MyComment{Possible Cross Site Scripting Attempt} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    WeBid LFI \MyComment{Local File Inclusion} & \cite{nikto} & LFI & http & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    %%WordPress Login & \cite{wrccdc} & PVE & http & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    .htaccess access\MyComment{attempted-recon} & \cite{nikto} & AREC & http \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & \cite{nikto} & AREC & http \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Basebuilder LFI & \cite{nikto} & LFI & http & \textbf{content}:"GET"; http\_method; \textbf{content}:"/main.inc.php?"; nocase; http\_uri; \textbf{content}:"mj\_config[src\_path]="; nocase; http\_uri; \\
    Tomcat Snoop Access & \cite{nikto} & AREC & http & \textbf{content}:"/jsp/snp/"; http\_uri; \textbf{content}:".snp"; http\_uri;\\  

>>>>

Figure~\ref{fig:adaptor-golden-rule.suricata} shows an example of an
http rule that captures traffic containing the string
\CodeIn{``/HtmlAdaptor''} in the payload.
Figure~\ref{fig:distribution-contents} shows the distribution of
number of content options per rule for the data set mentioned
above. We limited the number of content options per rule to 7 in the
histogram for space. \MyComment{Rules without \CodeIn{content} options
  are an exception and half of the rules contain at least two
  \CodeIn{content} options.}  To sum up, content options appear
frequently in http rules and rules may contain several of these
options. Handling content options is therefore very important.

@@

    %%Apache Struts 2 & \cite{wrccdc} & RCE & http & \textbf{content}:``POST''; http\_method; \textbf{content}:``java.lang.ProcessBuilder''; nocase; http\_client\_body; fast\_pattern; \textbf{content}:``/struts2-rest-showcase/orders/3''; http\_uri; \\    
    ColdFusion \MyComment{PESC} & \cite{nikto} & PESC & http \MyComment{& Privilege Escalation} & \textbf{content}:``GET''; http\_method; nocase; \textbf{content}:``/CFIDE/administrator''; http\_uri; nocase; \\
    iisadmin access\MyComment{web-application-attack} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:``/iisadmin''; nocase; http\_uri; \\
    JBoss JMX\MyComment{ Console Beanshell Exploit} & \cite{nikto} & RCE & http \MyComment{& Remote Code Execution} & \textbf{content}:``/HtmlAdaptor''; nocase; http\_uri; \textbf{content}:``action=inspect''; nocase; http\_uri; \textbf{content}:``bean''; nocase; http\_uri; \textbf{content}:``name=''; http\_uri; \\
    scripttag\MyComment{Possible Cross Site Scripting Attempt} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:``</script>''; nocase; http\_uri; \\
    WeBid LFI \MyComment{Local File Inclusion} & \cite{nikto} & LFI & http & \textbf{content}:``GET''; depth:4; \textbf{content}:``/cron.php?''; http\_uri; nocase; \textbf{content}:``include\_path=''; http\_uri; nocase; \textbf{content}:``''../''; \\
    %%WordPress Login & \cite{wrccdc} & PVE & http & \textbf{content}:``log=''; http\_client\_body; \textbf{content}:``''\&pwd=''; http\_client\_body; \textbf{content}:``''\&wp-submit=''; http\_client\_body; \\
    .htaccess access\MyComment{attempted-recon} & \cite{nikto} & AREC & http \MyComment{& Adicionar} & \textbf{content}:``.htaccess''; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & \cite{nikto} & RCE & http \MyComment{& Adicionar} & \textbf{content}:``.idq''; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & \cite{nikto} & AREC & http \MyComment{& Adicionar} & \textbf{content}:``/system32/''; nocase; http\_uri; \\
    Basebuilder LFI & \cite{nikto} & LFI & http & \textbf{content}:``GET''; http\_method; \textbf{content}:``/main.inc.php?''; nocase; http\_uri; \textbf{content}:``mj\_config[src\_path]=''; nocase; http\_uri; \\
    Tomcat Snoop Access & \cite{nikto} & AREC & http & \textbf{content}:``/jsp/snp/''; http\_uri; \textbf{content}:``.snp''; http\_uri;\\  
